---
title: "Notes for Databrary repo"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
params:
  download_video: false
---


# Purpose

This document describes information required to curate a Databrary volume for the "Face-off" paper project.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
source("R/write_video_clip_html.R")

# Clean-up mov/ directory
file.remove(list.files("mov", "\\.mp4$", full.names = TRUE))
```

## Logging in to Databary

```{r, eval=FALSE}
databraryapi::login_db()
```

# Background

A video from the [Play & Learning Across a Year (PLAY) project](https://play-project.org) was selected from among the pilot sessions.

[Participant 19](https://nyu.databrary.org/volume/444/slot/18825/-) from volume 444 was selected.

The 1 hour free play video (https://nyu.databrary.org/slot/18825/78777000,82445800/asset/85849/download?inline=true) was chosen for analysis.

A 3 min subset of this video beginning at 23:00 + ~ 4 frames was chosen for detailed coding and analysis.

```{r}
slot_id <- 18825
asset_id <- 85849
vol_id <- 444
frames_fr_23min <- 4
```

## Calculating the offset in milliseconds

```{r}
fps <- 29.97
secs_per_min <- 60
ms_per_sec = 1000
vid_start_ms <- 78777000
seg_start_offset_ms <- round((23*secs_per_min + frames_fr_23min/fps)*ms_per_sec)
seg_start_ms <- vid_start_ms + seg_start_offset_ms
seg_end_ms <- seg_start_ms + 3*secs_per_min*ms_per_sec
segment_id = paste0(seg_start_ms, ',', seg_end_ms)
```

If these calculations are correct, this should create the URI and download the relevant segment.

```{r}
(video_uri <- paste0("https://nyu.databrary.org/slot/", slot_id, "/", segment_id, "/asset/", asset_id, "/download?inline=true"))
```

If the `download_video` parameter is true this will download the video and display it. FIX: Wait until download is finished:

```{r, results='asis'}
if (params$download_video) {
  databraryapi::download_video(session_id = 18825, asset_id = 85849, 
                               segment_id = paste0(seg_start_ms, ',', seg_end_ms), out_dir = "mov")
  vids <- list.files("mov", pattern = "\\.mp4$", full.names = TRUE) 
  write_video_clip_html(vids[1])
}
```

This code should display the segment from Databrary inline.

```{r, results = 'asis'}
write_video_clip_html(video_uri)
```

# Clean-up

```{r}
databraryapi::logout_db()
```

